The focus is on the security aspects of autonomous vehicles, in particular the cybersecurity threats, standards, and industry practices used to secure these systems.
This review will not cover the ethical implications or the differences between human-driven and autonomous vehicles in terms of accidents and fatalities.

\subsection{Historical roots}\label{subsec:historical-roots}

The development of autonomous vehicles is a significant milestone in the evolution of intelligent transport systems.
It is important to start with some historical context to understand the current state of autonomous vehicles and then,
the security implications.

Vehicle automation has roots dating back to 1918 (Pendleton et al., 2017),
with General Motors showcasing the first concept of an automated vehicle in 1939 (Shladover, 2018).
Initial R\&D efforts were led by General Motors and the Radio Corporation of America Sarnoff Laboratory in the 1950s
(Shladover, 2018).
From 1964 to 2003, various government and academic initiatives in the US, Europe,
and Japan focused on automated buses, truck platoons, and advanced driving systems
(Shladover, 2018).
A significant boost came from DARPA’s Grand Challenges Program in the 2000s \cite{darpa_grand_challenges_book},
where AVs first navigated desert terrains in 2005 and urban roads by 2007 (Pendleton et al., 2017; Shladover, 2018).

Since then, researchers have rapidly progressed in academia and industry.
Volvo, Tesla, Audi, BMW,
Mercedes-Benz and Nissan are some of the major car manufacturers that have invested in AV technology \cite{faisal2019understanding}.

\subsection{Background of Autonomous Vehicles}\label{subsec:background-and-significance-of-autonomous-vehicles}
\subsubsection{Levels of Automation}\label{subsubsec:levels-of-automation}
\subsubsection{Communication}\label{subsubsec:communication}
\subsubsection{Perception}\label{subsubsec:perception}
\subsubsection{Software}\label{subsubsec:software}

\subsection{Autonomous Vehicle nowadays}\label{subsec:autonomous-vehicles-nowadays}

\subsection{Cybersecurity in AVs}\label{subsec:cybersecurity-in-avs}

\subsection{Motivation}\label{subsec:motivation}

\subsection{Social implications}\label{subsec:social-implications}

This section aims to provide a little insight into the social implications of autonomous vehicles.
The introduction of autonomous vehicles (AVs) is expected to have a profound impact on society \cite{thomas2020perception}, transforming transportation systems \cite{intelligent_transportation_2023}
, urban planning \cite{impact_autonomous_vehicles_2018}, and the economy \cite{economic_aspects_2020}.

\subsection{Structure of the Survey}\label{subsec:structure-of-the-survey}
