\subsection{Premises}\label{subsec:premises}

In this review,
I aim to provide a comprehensive overview of the research current state on security in autonomous vehicles.
My focus is on the key cybersecurity threats, standards, and industry practices in the field,
keeping in mind that the landscape is rapidly evolving.
The goal is to identify the most critical challenges and opportunities for future research in this area
and underline the importance of a multi-layered approach to cybersecurity in AVs, starting from the design phase.
The ethical implications of the technology or the comparison between human-driven and autonomous vehicles in terms of accidents and fatalities will not be covered.

\subsection{Research Question}\label{subsec:research-question}

Starting from the main threats in terms of cybersecurity regarding AV, the review will analyze the main actual opportunities to improve and regulate the security of these systems.
After that, the review will focus on the industry practices concluding in the future trends and emerging technologies that could enhance and simplify the security process of AVs.
The goal of this review is to address the following research questions:

\begin{enumerate}
    \item \textit{What are the most significant cybersecurity threats facing autonomous vehicles, and how these threats evolve with advancements in vehicle-to-everything (V2X) communication and other emerging technologies?}
    ""This question aims to identify specific types of attacks (e.g., sensor spoofing, remote hijacking, and data breaches) and their implications for the safety and functionality of autonomous vehicles.
    It should guide a thorough analysis of the threat landscape.""

    \item \textit{What existing standards and regulatory frameworks govern cybersecurity by design in autonomous vehicles, and how effectively do they address current and future security challenges?}

    ""This question focuses on evaluating the current standards (such as ISO/SAE 21434 and UNECE WP.29) to determine whether they sufficiently cover security needs across the lifecycle of autonomous vehicle development""

    \item \textit{What cybersecurity solutions and practices have been implemented by autonomous vehicle manufacturers, and how do they align with best practices in secure software development and system resilience?}

    ""This question seeks to explore the practical approaches taken by leading manufacturers (e.g., Tesla, Waymo) in integrating security measures into their systems, such as intrusion detection, secure over-the-air (OTA) updates, and encryption.
    \item \textit{What future trends and emerging technologies, such as artificial intelligence and blockchain, are being explored to enhance the cybersecurity of autonomous vehicles, and what challenges do they pose in real-world applications?}
    ""This question addresses the forward-looking aspect of autonomous vehicle security, examining innovative solutions that could improve security but also introduce new risks or technical hurdles.""
\end{enumerate}

\subsection{Selection Criteria}\label{subsec:selection-criteria}

The selection criteria for the literature review are as follows:
\begin{enumerate}
    \item \textit{Relevance:} The literature must be directly related to the topic of security in autonomous vehicles, focusing on cybersecurity threats, standards, and industry practices.
    \item \textit{Quality:} The literature should be published in reputable journals, conference proceedings, or books, ensuring high academic and technical standards.
    \item \textit{Recency:} The literature should be recent (published within the last five years) to reflect the latest developments in the field.
    \item \textit{Diversity:} The literature should cover a broad range of topics within the field of autonomous vehicle security, including but not limited to threat modeling, risk assessment, secure software development, and hardware security.
    \item \textit{Accessibility:} The literature should be accessible online or through academic libraries to ensure that it can be reviewed and cited effectively.
\end{enumerate}

Some references are not recent, but they are fundamental to understanding the historical context and the evolution of autonomous vehicles.

\subsection{Search Strategy}\label{subsec:search-strategy}

The search strategy for this review involved a systematic exploration of electronic databases, books, and relevant publications.

The following databases were used to identify relevant literature:

\begin{enumerate}
    \item IEEE Xplore
    \item WebOfScience
    \item SpringerLink
    \item Google Scholar
\end{enumerate}

Multiple searches were conducted, initially to discover in general the state of the art in the field of autonomous vehicles and then to focus on the security aspects.
The search terms used included combinations of the following keywords:
\textit{autonomous vehicles}, \textit{self-driving cars}, \textit{cybersecurity}, \textit{security threats}, \textit{standards}, \textit{industry practices}, \textit{V2X communication}, \textit{ISO/SAE 21434}, \textit{UNECE WP.29}, \textit{secure software development}, \textit{intrusion detection}, \textit{over-the-air updates}, \textit{encryption}, \textit{artificial intelligence}, and \textit{blockchain}.

Some principal queries were:
\begin{enumerate}
    \item \textit{autonomous vehicles cybersecurity threats}
    \item \textit{autonomous vehicles cybersecurity standards}
    \item \textit{autonomous vehicles cybersecurity connectivity}
    \item \textit{autonomous vehicles cybersecurity perception sensors}
    \item \textit{autonomous vehicles cybersecurity architecture}
    \item \textit{autonomous vehicles cybersecurity accidents}
    \item \textit{autonomous vehicles cybersecurity V2V, V2I, V2X}
    \item \textit{autonomous vehicles cybersecurity TODO}
    \item \textit{autonomous vehicles cybersecurity future trends}
    \item \textit{secure software development lifecycle autonomous vehicle}
    \item \teextit{autonomous vehicles secure over-the-air}
\end{enumerate}

Moreover, some filter was applied to search only recent results, only peer-reviewed articles, and only articles in English.
First, the search was conducted on IEEE Xplore and Google Scholar, and then the same search was replicated on the other databases to ensure the comprehensiveness of the results.

The search strategy aimed to identify a diverse range of sources, including academic papers, conference proceedings, books, and industry reports, to provide a comprehensive overview of research on security in autonomous vehicles.
In certain cases, the limit on the age of the publication was removed to include fundamental works that are not recent but representative of a specific technology or approach (think about CAN bus).
Moreover, some references are relative to the automotive industry in general, but they are fundamental to understanding the context in which autonomous vehicles are developed.

\subsubsection{Phases}\label{subsubsec:phases}
The search of papers and documents was conducted in two phases:
\begin{enumerate}
    \item \textit{General Search:} The initial search aimed to identify the main topics and subtopics related to security in autonomous vehicles.
    \item \textit{Focused Search:} The second search focused on specific aspects of cybersecurity in autonomous vehicles, such as threats, standards, industry practices, and future trend.
\end{enumerate}

Every search was conducted using the same keywords and filters.
To ensure consistency and comparability of results across different databases, in particular, the keywords \textit{autonomous vehicles} and \textit{cybersecurity} were always present in the search query to keep the focus on the main topic of the review.
Only for the~\ref{sec:future-trends} section, the year of publication was restricted to the last 2 years to ensure the most recent results and approaches.


\subsection{Quality Assessment}\label{subsec:quality-assessment}
The quality assessment of the selected literature has been differentiated based on the type of citation.
For books, the evaluation has been based on the reputation of the author and the publisher, considering both their academic credentials and contributions to the field.
Additionally, the relevance of the book to the specific topics of cybersecurity and autonomous vehicles has been taken into account.

Given the interdisciplinary nature of this topic, papers from social sciences and related fields have also been included.
The grade of confidence for principal papers has been evaluated based on several factors: the demonstration of results, coherence of conclusions, and the methodology employed.
A rigorous methodology is essential for ensuring validity and reliability in research findings, as highlighted by [source 1] and [source 2].

Furthermore, peer-reviewed journal articles have been prioritized due to their critical review process, which enhances the credibility of the research.
Articles that provide empirical data or case studies have been weighted more heavily, as they offer concrete evidence to support theoretical claims.
The citation index and impact factor of journals have also been considered to gauge the influence of the research within the academic community.

In cases where studies span multiple disciplines, a qualitative analysis was conducted to assess the applicability of their findings to cybersecurity in autonomous vehicles.
This approach ensures a comprehensive understanding of the topic, acknowledging the complexity of cybersecurity challenges that intersect with social, ethical, and technological dimensions.


\subsection{Data Extraction}\label{subsec:data-extraction}

The data extraction process involved identifying key information from the selected literature to address the research questions.
The following data points were extracted from each source:
\begin{enumerate}
    \item \textit{Publication:} The title of the publication, including the journal, conference, or book where the work appeared.
    \item \textit{Year:} The publication year to determine the recency of the source.
    \item \textit{Research Focus:} A brief summary of the main research focus or objective of the publication.
    \item \textit{Key Findings:} The primary findings or results of the research, including any significant insights or conclusions.
    \item \textit{Methodology:} The research methodology employed in the study, such as case studies, surveys, experiments, or theoretical analysis.
    \item \textit{Relevance:} The relevance of the publication to the research questions and the broader topic of security in autonomous vehicles.
\end{enumerate}

\subsection{Limitations}\label{subsec:limitations}

The limitations of this review include the following:
\begin{enumerate}
    \item \textit{Scope:} The review focuses primarily on cybersecurity threats, standards, and industry practices in autonomous vehicles, excluding ethical, legal, and social implications.
    \item \textit{Recency:} Due to the rapidly evolving nature of the field, some of the literature may not capture the most recent developments in autonomous vehicle security.
    \item \textit{Accessibility:} The availability of certain publications may be limited, but access to academic databases and libraries minimized the issue.
    \item \textit{Interdisciplinary nature:} The interdisciplinary nature of the topic may present challenges in synthesizing findings from diverse fields, but efforts have been made to ensure a comprehensive and holistic review.
\end{enumerate}

\newpage
